PHAT RAID, yo

### 2014-05-12 paper/paper.tex
Explain the three behaviors we use

\usepackage[sc,osf]{mathpazo}
\linespread{1.05}         % Palatino needs more leading (space between lines)
\usepackage[T1]{fontenc}

@@

The \texttt{supervisor} behavior simply provides a framework for restarting failed
processes.

The \texttt{gen\_server} behavior provides a framework

>>>>

\usepackage[sc,osf]{mathpazo}
\linespread{1.05}         % Palatino needs more leading
\usepackage[T1]{fontenc}

@@

\begin{itemize}
\item The \texttt{supervisor} behavior provides a framework for restarting
  failed processes.
\item The \texttt{gen\_server} behavior provides a framework for many-client
  single-server interactions. We implemented functions to process messages
  formatted as Erlang tuples. The \texttt{gen\_server} behavior handles
  low-level socket interaction.
\item The \texttt{gen\_fsm} behavior generalizes the \texttt{gen\_server}
  behavior by permitting the server to have a finite number of states. Each
  state has a set of functions with which to process messages. This behavior can
  be seen as an ad hoc polymorphic variant of the \texttt{gen\_server} behavior.
\end{itemize}

Additionally, the \texttt{gen\_server} and \texttt{gen\_fsm} behaviors allow
the programmer to specify an arbitrary state value which will be passed around
\`{a} la functional reactive programming.
